Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2023-08-21 writing/CONUS_AOD.qmd
Cleaned up a plot axis.

```{r shap_features, dev='png', dpi=300}
g1 <- shap.plot.dependence(data_long = shap_long, x = 'time.sat', y = 'Column_WV', color_feature = 'Column_WV') + ggtitle("(A) SHAP values of Column WV vs. Time trend")
# g2 <- shap.plot.dependence(data_long = shap_long, x = 'time.sat', y = 'y.sat', color_feature = 'y.sat') +  ggtitle("(B) SHAP values of MAIAC AOD vs. Time trend")
#
# gridExtra::grid.arrange(g1, g2, ncol = 2)
g1
```

>>>>

```{r shap_features, dev='png', dpi=300}
g1 <- shap.plot.dependence(data_long = shap_long, x = 'time.sat', y = 'Column_WV', color_feature = 'Column_WV') +
    aes(x = lubridate::as_datetime(x_feature)) +
    xlab("time.sat") +
    ggtitle("(A) SHAP values of Column WV vs. Time trend")
# g2 <- shap.plot.dependence(data_long = shap_long, x = 'time.sat', y = 'y.sat', color_feature = 'y.sat') +  ggtitle("(B) SHAP values of MAIAC AOD vs. Time trend")
#
# gridExtra::grid.arrange(g1, g2, ncol = 2)
g1
```
